IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-10-16 paper/intro.tex
Intro

To reason about our monitor, we introduce a \emph{generic} formalism which
translates coarse-grained IFC ideas~\cite{Zeldovich:2006} into a language-based
setting: an information flow control system should be thought of as multiple
instances of \emph{completely isolated language runtimes} or \emph{tasks}, with
information flow control applied to inter-task communication.
% We describe a
% formal framework in which an IFC system can be designed once and then applied to
% any programming language which has control over external effects like
% JavaScript.
%(e.g., JavaScript) or C with access to hardware privilege separation).
We formalize our framework by using the Matthews-Findler's
approach~\cite{Matthews:2007:OSM:1190216.1190220} for combining operational
semantics and prove non-interference guarantees that are independent of the
choice of the specific underlying programming language, e.g., JavaScript.
%framework to , being one instead of
%that ECMAScript. %target language.

>>>>

To reason about our monitor, we introduce a \emph{generic} formalism which
translates coarse-grained IFC ideas~\cite{Zeldovich:2006} into a language-based
setting: an information flow control system should be thought of as multiple
instances of \emph{completely isolated language runtimes} or \emph{tasks}, with
information flow control applied to inter-task communication.
% We describe a
% formal framework in which an IFC system can be designed once and then applied to
% any programming language which has control over external effects like
% JavaScript.
%(e.g., JavaScript) or C with access to hardware privilege separation).
We formalize our framework by using the Matthews-Findler's
approach~\cite{Matthews:2007:OSM:1190216.1190220} for combining operational
semantics and prove non-interference guarantees that are independent of the
choice of the specific underlying programming language. %, e.g., JavaScript.
%framework to , being one instead of
%that ECMAScript. %target language.
